
\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1cm, right=2cm, bottom=2cm, footskip=.2cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts
 
% Color for highlights
\colorlet{awesome}{awesome-skyblue} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Lukáš}{Forst}
\address{Mrákov, Pilsen region, Czech Republic}
\mobile{+420 721 680 117}

\email{lukas@forst.pw}
\github{LukasForst}
\linkedin{lukas-forst} 
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}
% \linkedin{Lukas Forst}
%\reddit{reddit account}
%\xing{xing name}
%\extrainfo{test} % Other text you want to include on this line

\position{Software Engineering student{\enskip\cdotp\enskip}Software Engineer{\enskip\cdotp\enskip}Tech Lead} % Your expertise/fields
% \quote{``Make the change that you want to see in the world."} % A quote or statement

\makecvfooter{\today}{Lukas Forst~~~·~~~Cover Letter}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------o
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{IT University of Copenhagen}{Rued Langgaards Vej 7, 2300 København, Denmark} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{ITU Application} % The title of the letter

\letteropening{Dear Sir, Madam} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

% \letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title


\begin{cvletter}

%------------------------------------------------

\lettersection{About Me}
I'm writing to apply for the MSc programme on IT University in Copenhagen. 
This year I will hopefully finish the Faculty of Electrical Engineering on Czech Technical University in Prague in Open Informatics programme 
with focus on Software Engineering and Artificial Intelligence and
thus I'm seeking new challenging opportunities in computer science field, which led me to this application.
I'm currently working on my bachelor thesis which aim is to introduce brand new load balancing mechanism tailored specifically for optimization algorithms.
This solution is based on the mathematical model of runtime optimization techniques represented as integer linear programming as well as 
bleeding edge technologies used in the implementation of my custom optimization load balancer. 
Effectively, it should cut hardware resources cost paid while hosting application which contains optimization algorithm.

In the second semester of my study at FEE, 
my professor personally hired me into his university spin-off AI company, now called Blindspot Solutions,
because he saw potential in my software development skills for nex two years I was youngest member of the team.
Since then I worked on multiple projects for clients all over the world and designed various kinds of software systems.
Working 2 years with bleeding edge technologies in the industry leading AI company with international team developing machine learning and optimization solution for all over the world customers. 
Now I'm personally leading the team working on the state of the art scheduling system for major Chinese investor.
My working experience are not only from the Czech Republic,
I was also working in the Paris at Softbank Robotics Headquater with the next-gen robot Pepper as a member of team sent by slovakia branch of world wide business consulting company Adastra.


\lettersection{Why ITU?}
I'm genuinely interested in Danish culture since my ancestors came to the Czechia from Denmark.
When I was on vacation in Copenhagen las year,
I had a chance to visit ITU and I was surprised by the student culture and genius loci of the campus.
I went trough the offered programmes and I found out that Computer Science programme perfectly suits to my expectations 
of well prepared and balanced, in terms of business and technical education, academic course.
Also I believe, that study at ITU would bring me all necessary knowledge for my future professional carrier in computer science field.


\lettersection{Why Me?}
While I was studying at the grammar school in 2015, I was placed third in the national wide Computer Science related competition, 
this resulted into my nomination to various types of international events. 
For example, I was representative of the Czech Republic on the Swiss Talent Forum 2017 in Bern where I gained necessary skills in business development 
and team leadership.
I believe that I can be an asset to the university mainly because of my experience with real life software engineering, business development and my strong mathematical background.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}
