\cvsection{Experience}

\begin{cventries}
		
	\cventry
	{Software Engineer}
	{Blindspot Solutions s.r.o.}
	{Prague, Czech Republic}
	{June 2017 - PRESENT}
	{
		\begin{cvitems}
			\item {
				Member of the team (five people) that designed and developed distributed platform executing, running, and scaling big optimization jobs. 
				The platform is built upon microservice architecture, and it is written in Kotlin. It is deployed in the Azure cloud and runs on Kubernetes. 
			 	As database serves MS SQL and for the communication between microservices utilizes Azure Service Bus. 
			 	Another used technologies in this platform are Azure Container Registry, Azure Blob Storage, and Gradle.
			 	\newline
			 	My responsibility during this project was to develop various features such as a platform to docker-machine communication and many others.
				I was also designing and developing several DevOps operations and pipelines 
				(unit testing and quality assurance pipelines as well as integration ones).
				Thanks to my previous experience with Kotlin, I was helping team members to learn the language and was supervising the code reviews.
			}
			\item {
				I was a member of the team (two developers, one optimization engineer) developing a factory production optimization engine
				for a major European car manufacturer. 
				The application's dev-stack consists of Kotlin, Spring Boot, Hibernate, Maven, Docker, Docker-Compose, Oracle 12c, SAP Hana. 
				The application was deployed in the client's infrastructure as well as on the AWS.
				\newline
				I was responsible for project integration to the client's infrastructure and flawless communication with legacy systems 
				and various types of databases.
				During this project, I developed a custom Kotlin written solution based on typesafe reflection for communication
				between SAP Hana's stored procedures and an in-house optimization engine.
			}
			\item {
				Member of the team (three to six people) that developed application utilizing state of the art optimization core 
				for inspection scheduling for a significant Chinese auditing company. 
				This project used C\#, .NET 4.7.2, Entity Framework, LINQ, MS SQL, Sharepoint and REST integration.
				\newline
				For the first months of the project, I was working on the overall system refactoring and implementing minor features.
				Later on, I was responsible for the maintenance and bug fixing of the import pipelines from the client's Sharepoint legacy system.
				During the system's extension, I redesigned, implemented, and tested the new import pipelines that were importing data 
				from multiple instances of various Sharepoints from the client's infrastructure.
				\newline
				After the project transformation a two years later, I was a tech lead of the team of four people, 
				that was modifying the import layer and connecting it to different client's system. 
				I communicated with the client and with the technic team implementing their system and ultimately designing REST APIs for both sides.
			}
		\end{cvitems}
	}
	
	\cventry
	{IT Assistant}
	{APM Automotive s.r.o.}
	{Kdyně, Czech Republic}
	{June 2016 - September 2016}
	{
		\begin{cvitems}
			\item {
				Development of C\# based programme which exported/converted the list of individual stock items from the Excel files
			 	to the html file and enabled instant web search for photographs of the items and simplified the stock keeping process.
			 }
		\end{cvitems}
	}
			
\end{cventries}